Automated Topic Naming

### 2012-01-16 ese/ese.tex
- [X] On page 9 you mention that you put the term "redundancy" under the          flag of reliability. This is quite possible in the context of RDBMS,          but... it could also be used to indicate code cloning (code          redundancy). How did you cope with this double meaning?          Threat to validity and IRR issues

Our second word-list, \textsf{exp2}, uses the ISO9126 taxonomy described above (Section \ref{sec:wordlist}) to seed the word-lists.
%We use these qualities later on as classes in supervised labelling. NE confusing the issue here, I think.
The terms from ISO9126 may not capture all words occurring in the topics that are nonetheless associated with one of the NFRs. 
For example, the term ``redundancy'' is one 
we considered to be
relevant to discussion of \emph{reliability}, but is not in the standard. 
We therefore took the NFRs from the ISO9126 and added terms to them.

@@

>>>>

Our second word-list, \textsf{exp2}, uses the ISO9126 taxonomy described above (Section \ref{sec:wordlist}) to seed the word-lists.
%We use these qualities later on as classes in supervised labelling. NE confusing the issue here, I think.
The terms from ISO9126 may not capture all words occurring in the topics that are nonetheless associated with one of the NFRs. 
For example, the term ``redundancy'' is one 
we considered to be
relevant to discussion of \emph{reliability}, but is not in the
standard. We recognize though that terms like this might be used in a
different context with a different meaning, like code-cloning.
We therefore took the NFRs from the ISO9126 and added terms to them.

@@

Our word-lists were built up of words that were assumed to be relevant
to those topics, our automated analysis was ignorant of the multi-uses
of words and thus topics could be flagged inappropriately. For
instance, if the word \emph{redundancy} is used would it reference
reliability or cloned code? This issue is why we checked the
performance of the techniques, although we did not explicitly check
for these cases.
